Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
merge

\paragraph{Varargs}
Arguments that are part of a function's varargs (denoted \VARGS) are
ignored, as type \any is output for the entire varag construct.

@@

\input{tables/uni-typed-breakdown.tex}
Figure~\ref{fig:singlefreq} provides a breakdown of the different type categories
observed at uni-typed positions. Scalar, class and vector are
the most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of \CountPositions
parameter and return positions.

@@

Figure 1 shows the number of alternatives in the inferred type of function
parameter and return values.

XXX\% of the parameter positions are monomorphic.  \typetracer observes XXX
calls to XXX functions with XXX arguments. This translates to XXX parameters
and XXX return types.  A parameter or return type is from unioning all the
distinct observed types of

Figure 1 shows the distribution of parameter and return types for these
functions.

>>>>

\paragraph{Varargs}
Arguments that are part of a function's varargs (denoted \VARGS) are
ignored, as type \VARGS is output as the type of the entire varargs construct.

@@

\input{tables/uni-typed-breakdown.tex}
Table~\ref{fig:singlefreq} provides a breakdown of the different type categories
observed at uni-typed positions. Scalar, class and vector are
the most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of \CountPositions
parameter and return positions.

@@
